### 2016-10-25 paper/evaluation.tex
Added piechirt

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t <
    10m$), very long execution ($10m \leq t$).}
\end{figure}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
    \caption{\label{fig:timetests-scatter} \Fix{...}}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:timecost-barplot} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), normal
    execution ($1m \leq t < 5m$), long execution ($5m \leq t <
    10m$), and very long execution ($10m \leq t$).}
\end{figure}

@@

%% \begin{figure}[t!]
%%     \centering
%%     \includegraphics[width=0.5\textwidth]{plots/teststime-scatter/timetests-scatter.pdf}
%%     \caption{\label{fig:timetests-scatter} \Fix{...}}
%% \end{figure}
